Addendum to a survey of HTTP caching on the Semantic Web

### 2015-03-20 sanity/report.tex
Minor changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1107 43ef1190-90fd-4dd7-a769-d0121f02b80e

The BTC2014 dataset provided data in the form of NQuad files. Due to
the presence of invalid RDF, we iterated through the NQuad files on a
line-by-line basis. First, we matched each line against a regular
expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011}
was used to parse the line. Lines that failed to parse were
discarded. We have not investigated whether this could introduce
biases. Statements were then accepted into a new NQuad file if they
had a predicate that matched the \rdfterm{sd:endpoint} or matched a
case-insensitive regular expression \texttt{sparql} if the subject and
objects were both resources, or the predicates
\rdfterm{void:vocabulary}, \rdfterm{rdfa:vocabulary}, or
\rdfterm{api:vocabulary}, as well as having a resource as
object. Finally, statements with the the classes
\rdfterm{cogs:Endpoint}, \rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary} in the object position were also
accepted\footnote{Linked Open Vocabularies \cite{lov2} may be used to
  resolve these prefixed names}. More classes and properties were
considered, but not used in the data reduction if they did not occur
in the original data.

@@

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}
to CPAN. We recorded whether the conditional request showed that the
BTC2014 data were still fresh, and if it was, we retrieved the current
data, as we had not coupled the headers to the body in our original
retrieval.  Based on the resulting headers, we let
libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}
calculate both standards-compliant and simple heuristic freshness
lifetime.

@@

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are. In addition
to the endpoints registered in the SPARQLES survey, our process found
18~endpoints that responded with results. For all others, we parsed
the response, and recorded any errors if the parser concluded the
content were invalid.

@@

@@

\todo{qqplot in report}.

>>>>

The BTC2014 dataset provided data in the form of NQuad files. Due to
the presence of invalid RDF, we iterated through the NQuad files on a
line-by-line basis. First, we matched each line against a regular
expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{\url{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011}}
was used to parse the line. Lines that failed to parse were
discarded. We have not investigated whether this could introduce
biases. Statements were then accepted into a new NQuad file if they
had a predicate that matched the \rdfterm{sd:endpoint} or matched a
case-insensitive regular expression \texttt{sparql} if the subject and
objects were both resources, or the predicates
\rdfterm{void:vocabulary}, \rdfterm{rdfa:vocabulary}, or
\rdfterm{api:vocabulary}, as well as having a resource as
object. Finally, statements with the the classes
\rdfterm{cogs:Endpoint}, \rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary} in the object position were also
accepted\footnote{Linked Open Vocabularies \cite{lov2} may be used to
  resolve these prefixed names}. More classes and properties were
considered, but not used in the data reduction if they did not occur
in the original data.

@@

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{\url{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}}
to CPAN. We recorded whether the conditional request showed that the
BTC2014 data were still fresh, and if it was, we retrieved the current
data, as we had not coupled the headers to the body in our original
retrieval.  Based on the resulting headers, we let
libwww\footnote{\url{https://metacpan.org/release/GAAS/libwww-perl-6.04}}
calculate both standards-compliant and simple heuristic freshness
lifetime.

@@

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are. In addition
to the endpoints registered in the SPARQLES survey
\cite{buil2013sparql}, our process found 18~endpoints that responded
with results. For all others, we parsed the response, and recorded any
errors if the parser concluded the content were invalid.

@@

Since the same test can be used for binned data in many different
situations, we used it more informally in other parts of the paper as well.

@@

Since web servers may be configured to instruct clients and proxies to
cache errors differently from successfully served requests, it is
interesting to investigate whether we can simply use all cache headers
in the analysis, or if we should remove unsuccessful responses to
avoid introducing bias to the analysis of valid responses.

For a visual inspection, we may use a quantile-quantile plot to plot
the freshness lifetimes of successful responses versus requests that
failed for some reason. If the distribution of both variables are the
same, these points will lie on a straight line. In
Figure~\ref{fig:errorsqq}, we see successful responses vs. the most
common parse error, and it is clear that these are so different that
no further formal analysis is necessary. This is one of the reasons
why we filtered unsuccessful requests before we analyzed the freshness
lifetimes in the paper.

\begin{figure}[h]
  \centerline{%
    \includegraphics[width=.8\textwidth]{errorsqq.pdf}}
  \caption{A quantile-quantile plot of freshness lifetimes for
    standard compliant headers with and without errors.}
  \label{fig:errorsqq}
\end{figure}
